|

### 2016-05-23 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

```{r, echo = F, include=F}
library(mzID)
evalue = 1e-10
pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide", "Protein")]
p3_flt <- flatten(mzid_p3)
bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")], by.x="Scan", by.y = "scan number(s)", all.x = T)
```

@@

#4. Result from MSGF+ without any switches (sorted by SpecEValue)
```{r, echo=F}
tmp           <- ns_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
## Looking at Scan Number 11612 and 14441
tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]
```

@@

# 5. Results with switches
```{r, echo=F}
tmp           <- p3_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")])[1:3,])
## Looking at Scan Number 11612 and 14441
tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441") &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]

@@

Reading the MZID file manually
```{r, echo=F}
head(tsv)[1:3,c("ScanNum", "Peptide", "Protein", "SpecEValue")]
```

@@

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq", "accession")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

@@

>>>>

```{r, echo = F, include=F}
library(mzID)
evalue = 1e-10
pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
p3_flt <- flatten(mzid_p3)
bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
```

@@

#4. Result from MSGF+ without any switches (sorted by SpecEValue)
```{r, echo=F}
tmp           <- ns_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue",  "pepseq")])[1:3,])
## Looking at Scan Number 11612 and 14441
tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441")  &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "pepseq")]
```

@@

# 5. Results with switches
```{r, echo=F}
tmp           <- p3_table
tmp           <- tmp[order(tmp$'ms-gf:specevalue'),]
show(head(tmp[,c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "pepseq")])[1:3,])
## Looking at Scan Number 11612 and 14441
tmp[(tmp$`scan number(s)`=="11612" | tmp$`scan number(s)`=="14441") &! is.na(tmp$`scan number(s)`),c("scan number(s)", "ms-gf:denovoscore", "ms-gf:specevalue", "accession", "pepseq")]

@@

Reading the MZID file manually
```{r, echo=F}
head(tsv)[1:3,c("ScanNum", "Peptide", "SpecEValue")]
```

@@

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

@@

# 7. Filtering
```{r, include=F}
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
```

### From Docker 
```{r echo=F}
tmp <- (p3_table[p3_table$'ms-gf:specevalue'<evalue & !is.na(p3_table$'ms-gf:specevalue'<evalue),c("scan number(s)", "ms-gf:specevalue", "pepseq")])
tmp <- tmp[order(tmp$`ms-gf:specevalue`),]
print("==Head==")
head(tmp,2)
print("==Tail==")
tail(tmp,2)

bt_tmp <- merge(y =  tmp, x=pnnl, by.x = "Scan", by.y  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.

Aside from the `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),],3)
print("==Tail==")
tail(bt_tmp,2)
```
